What Can Stack Traces Tell us about the Use of Exceptions in Java?

### 2014-05-09 android-stacks.tex
Remove hassanboxes for the moment

\noindent \fbox{
\begin{minipage}{0.96\columnwidth} \emph{ RQ1: 28,37\% of Java
  repositories on Github have at least 1 issue that includes a stack trace.
  9,4\% of the defect issues of such repositories mentioned at least one stack
  trace. Considering only defect-issues of Android subset 58,7\% mentioned at
  least 1 stack trace.  }
\end{minipage}}

@@

\begin{table}
  \centering
  \begin{tabular}{rp{22em}}
    \hline
    \bfseries{Type of signaler} & \bfseries{Description} \\
    \hline
    \bfseries{android} & If the exception is thrown by a method defined in Android Platform or OS, or in a JDK library used by them.\\
    \bfseries{app}     & If the exception is thrown by an application method or in a  DK library used by it.\\
    \bfseries{libcore} & If the exception is thrown by one of the core libraries reused by Android (i.e., org.apache.harmony, org.w3c.dom, sun.misc, org.apache.http, org.json, org.xml). \\
    \bfseries{lib}     & If the exception is thrown by a method that was not defined by any of the elements above.\\
    \bfseries{java}    & If all methods on the stack trace are JDK library methods.\\
    \hline
  \end{tabular}
  \caption{Sources of exceptions in Android}
  \label{tab:signalers}
\end{table}

@@

\noindent \fbox{
\begin{minipage}{0.96\columnwidth} 
\emph{RQ2: Most exceptions are due to programming mistakes
or generally irrecoverable errors.}
\end{minipage}}

>>>>

%\noindent \fbox{
%\begin{minipage}{0.96\columnwidth} \emph{ RQ1: 28,37\% of Java
%  repositories on Github have at least 1 issue that includes a stack trace.
%  9,4\% of the defect issues of such repositories mentioned at least one stack
%  trace. Considering only defect-issues of Android subset 58,7\% mentioned at
%  least 1 stack trace.  }
%\end{minipage}}

@@

\begin{table}
  \centering
  \begin{tabular}{rp{29em}}
    \hline
    \bfseries{Signaler} & \bfseries{Description} \\
    \hline
    \bfseries{android} & If the exception is thrown by a method defined in Android Platform or OS, or in a JDK library used by them.\\
    \bfseries{app}     & If the exception is thrown by an application method or in a  DK library used by it.\\
    \bfseries{libcore} & If the exception is thrown by one of the core libraries reused by Android (i.e., org.apache.harmony, org.w3c.dom, sun.misc, org.apache.http, org.json, org.xml). \\
    \bfseries{lib}     & If the exception is thrown by a method that was not defined by any of the elements above.\\
    \bfseries{java}    & If all methods on the stack trace are JDK library methods.\\
    \hline
  \end{tabular}
  \caption{Sources of exceptions in Android}
  \label{tab:signalers}
\end{table}

@@

%\noindent \fbox{
%\begin{minipage}{0.96\columnwidth} 
%\emph{RQ2: Most exceptions are due to programming mistakes
%or generally irrecoverable errors.}
%\end{minipage}}
